Molecular alignment at graphene surface determines tansport properties of graphene transistors

### 2020-04-03 manuscript.tex
Update manuscript.tex
I think we should round mobility.

not clearly understood the last sentence from the conclusion part

Firstly, we focus on the initial charge carrier density $n_0$, which stems from the impurities residing either at the graphene interface or within the gate dielectric. On clean graphene we obtained a value of 3.33$\times 10^{11}$ cm$^{-2}$, which may be considered a ``clean'' sample for long-range scattering.  As the coverage of PDI8-CN2 is increased to 0.7 $n_0$ exhibits only a slight increase to 3.71$\times 10^{11}$ cm$^{-2}$, but almost doubles at full coverage ($n_{0}=7.42\times 10^{11}$ cm$^{-2}$).
In order to explain the observed behavior, we have to consider the dependence of the electronic structure of organic thin layers on the molecular orientation.  Anisotropic behavior of charge transport properties of organic thin films are known for some time now\cite{sundar-2004}. Less common are detailed studies of the dependence of the position of the electron energy levels at different molecular orientation. This is particularly true for $n$-type OSs on graphene. Zhang et al.\cite{zhang-2016d} have performed a systematic photoelectron spectroscopy study coupled to density functional theory (DFT) -based calculations of electrostatic potential surfaces of several organic semiconductors including n-type. Their findings demonstrate energy shifts of the electronic structures as high as 0.54 eV between the layers with the molecules oriented upright and flat-lying molecules.  Crucial for such difference is the existence of the dipole (and quadrupole) electric field arising at different moieties of the molecules. For example, in the case of pyrrolo[3,4-c]pyrrole-1,4-dione (DPP)  the calculations show a surface electric dipole due to the electron-withdrawing carbonyl and imine groups pointing  away from the surface when the molecules are oriented upright (shorter molecular axis perpendicular to the surface). On the other hand flat-lying DPP molecules exhibit a quadrupole moment that points towards the surface. Consequently, the energy of HOMO is closer to the vacuum level in the case of flat-lying molecules relative to upright oriented molecules.

@@

Coupled to the change in the position of CNP is also an increase in the overall resistance of the structure. This is because for the OS layers the metallic contacts are of the  bottom-contact type, and charge transport occurs in parallel through graphene and the second layer of PDI8-CN8, in which $\pi$-stacking provides more favorable charge transporting lane than the flat-lying molecules. Overall resistance is therefore net resistance between graphene and PDI8-CN2. Interestingly the asymmetry in contact resistance for holes (R$_{h}$) and  electrons  (R$_{e}$) on clean graphene as obtained from the model is quite appreciable and reflects the qualitative arguments given above.  On fully covered graphene, when the charge transport proceeds also over PDI8-CN2 layer for which the contacts are of the bottom-type this asymmetry almost vanishes (R$_{e}$=2632 $\Omega$, vs. R$_{h}=2548\ \Omega$).  Coupled to the doping structure of the channel discussed above is also asymmetry in hole mobility  ($\mu_{h}= 26920$ cm$^{2}$/Vs ) and electron mobility ($\mu_{h}= 15772$ cm$^{2}$/Vs) on clean graphene. As the PDI8-CN2 layer is completed the mobility is drastically reduced relative to the clean graphene.  This argues for the opening of the charge transport venue through the second layer of $\pi-\pi$ molecular array. Transport is ambipolar and characterized by charge carrier mobility values that are unprecedented for an OS-graphene system.

>>>>

Firstly, we focus on the initial charge carrier density $n_0$, which stems from the impurities residing either at the graphene interface or within the gate dielectric. On clean graphene we obtained a value of 3.33$\times 10^{11}$ cm$^{-2}$, which may be considered a ``clean'' sample for long-range scattering.  As the coverage of PDI8-CN2 is increased to 0.7, $n_0$ exhibits only a slight increase to 3.71$\times 10^{11}$ cm$^{-2}$, but almost doubles at full coverage ($n_{0}=7.42\times 10^{11}$ cm$^{-2}$).
In order to explain the observed behavior, we have to consider the dependence of the electronic structure of organic thin layers on the molecular orientation.  Anisotropic behavior of charge transport properties of organic thin films are known for some time now\cite{sundar-2004}. Less common are detailed studies of the dependence of the position of the electron energy levels at different molecular orientation. This is particularly true for $n$-type OSs on graphene. Zhang et al.\cite{zhang-2016d} have performed a systematic photoelectron spectroscopy study coupled to density functional theory (DFT) -based calculations of electrostatic potential surfaces of several organic semiconductors including n-type. Their findings demonstrate energy shifts of the electronic structures as high as 0.54 eV between the layers with the molecules oriented upright and flat-lying molecules.  Crucial for such difference is the existence of the dipole (and quadrupole) electric field arising at different moieties of the molecules. For example, in the case of pyrrolo[3,4-c]pyrrole-1,4-dione (DPP)  the calculations show a surface electric dipole due to the electron-withdrawing carbonyl and imine groups pointing  away from the surface when the molecules are oriented upright (shorter molecular axis perpendicular to the surface). On the other hand flat-lying DPP molecules exhibit a quadrupole moment that points towards the surface. Consequently, the energy of HOMO is closer to the vacuum level in the case of flat-lying molecules relative to upright oriented molecules.

@@

Coupled to the change in the position of CNP is also an increase in the overall resistance of the structure. This is because for the OS layers the metallic contacts are of the  bottom-contact type, and charge transport occurs in parallel through graphene and the second layer of PDI8-CN2, in which $\pi$-stacking provides more favorable charge transporting lane than the flat-lying molecules. Overall resistance is therefore net resistance between graphene and PDI8-CN2. Interestingly the asymmetry in contact resistance for holes (R$_{h}$) and  electrons  (R$_{e}$) on clean graphene as obtained from the model is quite appreciable and reflects the qualitative arguments given above.  On fully covered graphene, when the charge transport proceeds also over PDI8-CN2 layer for which the contacts are of the bottom-type this asymmetry almost vanishes (R$_{e}$=2632 $\Omega$, vs. R$_{h}=2548\ \Omega$).  Coupled to the doping structure of the channel discussed above is also asymmetry in hole mobility  ($\mu_{h}= 26920$ cm$^{2}$/Vs ) and electron mobility ($\mu_{h}= 15772$ cm$^{2}$/Vs) on clean graphene. As the PDI8-CN2 layer is completed the mobility is drastically reduced relative to the clean graphene.  This argues for the opening of the charge transport venue through the second layer of $\pi-\pi$ molecular array. Transport is ambipolar and characterized by charge carrier mobility values that are unprecedented for an OS-graphene system.
